A Study on Penguins: A Minimal Reproducible Example

### 2024-08-21 01_Example/Manuscript.qmd
Fix whitespace

---
title: "A Study on Penguins: A Minimal Reproducible Example"
author:
  - name: "Kan Garoo"
    affiliation: "University of Melbourne"
    email: "kangaroo@email.com"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
bibliography: Bibliography.bib
format:
  #apaquarto-docx: default
  #apaquarto-html: default
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
    keep-tex: true
---

>>>>

---
title: "A Study on Penguins: A Minimal Reproducible Example"
author:
  - name: "Josephine Zerna"
    email: "josephine.zerna@tu-dresden.de"
    orcid: 0000-0003-2892-884X
    roles:
      - conceptualization
      - writing
    affiliations:
      - id: id1
        name: "Technische Universität Dresden"
        group: Chair of Differential and Personality Psychology
        department: Faculty of Psychology
        city: Dresden
        postal-code: 01069
  - name: "Christoph Scheffel"
    affiliation: 
      - id: id1
    email: "christoph_scheffel@tu-dresden.de"
    orcid: 0000-0001-5963-9229
    corresponding: true
    roles:
      - project administration
      - methodology
date: "`r format(Sys.Date(), '%B %d, %Y')`"
abstract: "This document is a minimal, reproducible manuscript using the penguins data set as an example."
keywords: [penguins, reproducibility, minimal, example]
floatsintext: false
bibliography: Bibliography.bib
format:
  #apaquarto-docx: default
  #apaquarto-html: default
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
    keep-tex: true
---
